Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/reviewers-response.Rmd

> "*Discussion*: 'species' strength'

*Accepted and changed*: In the Methods section we deine species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}). For brevity, we did not define it again in the Disussion, but now we have improved the text and briefly describe it when we mention it there too. The text now reads "When controlling for a species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance..." (\lr{M-R2-species-strength-b}).

> * "desired control trajectory " - does this mean "final state"?

> "'driver node density' (supp p12) -> 'size of the minimum driver node set'?"

### 2019-01-13 paper/supp-info.Rmd
Removing reference to driver node density

At a network scale the driver-node density $n_D$ was consistent among the three weighting schemes (`r round(bal_nd$eff, 2)` for deposition, `r round(bal_nd$vis, 2)` for the visitation, and `r round(bal_nd$imp, 2)` for the pollinator-importance network, respectively).
The choice of weighting can also have an impact on at the species level.
Therefore we calculated $\phi$ and $\sigma$ and calculated its correlation among all three weighting schemes.
Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-assumption-visitation)).

>>>>

At a network scale the size of the minimum driver node set $n_D$ was consistent among the three weighting schemes (`r round(bal_nd$eff, 2)` for deposition, `r round(bal_nd$vis, 2)` for the visitation, and `r round(bal_nd$imp, 2)` for the pollinator-importance network, respectively).
The choice of weighting can also have an impact on at the species level.
Therefore we calculated $\phi$ and $\sigma$ and calculated its correlation among all three weighting schemes.
Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-assumption-visitation)).
